Creating figures for the paper

### 2024-07-30 infercnv/reports/paper_figures.Rmd
add params, deal with NULL-> NA conversions
fix channel issues

# Plot 3 - inferCNV plot with all individuals together

>>>>

# Plot 4 - inferCNV plot with all individuals together

I am currently trying to run this. I have run into some issues with `inferCNV`
dependencies breaking on farm22, so this has been on hold for the last 2 weeks.

# Plot 5 - Mutation hotspots

We load Luke's object. The `nano_muts` are the targeted mutations. The 
`exome_muts` is a list of significant drivers in each cell type (dNdScv output).

```{r}
# load the metadata
sm <- readr::read_tsv("/lustre/scratch125/casm/team268im/lh22/Rheumatoid_Arthritis_Paper/Data/MetaData/sample_meta.tsv")

# load the muts and convert to list
load("/lustre/scratch125/casm/team268im/lh22/Rheumatoid_Arthritis_Paper/Figures/Figure_2/LCM_NanoSeq_Overlap/GOI/pileup_muts.rda")
muts <- list(exome = exome_muts,
             LCM = LCM_muts,
             targeted = nano_muts,
             pileup = pileup_muts)

# genes of interest
goi <- "NF1"

# get annotations from dndscv output
mut_annots <-
  muts$exome %>%
  tibble::as_tibble() %>%
  dplyr::select(chr, pos, gene, ref, mut, type, tri, impact, aachange)

muts$targeted %>%
  tibble::as_tibble() %>%
  dplyr::select()
```
